         Register  Gladiator!

  If you've enjoyed playing the
freeware version of Gladiator, please
consider registering for the
commercial version!

When you register, you'll get:
  *  Many more scenarios (take your
     guys to incredible levels!)
  *  A scenario editor -- make your own
  *  More special abilities (up to
     six per character -- almost 40
     in all)
  *  More types of characters, and the
     ability to purchase all of them
     for your team, including:
     - FIRE ELEMENTALS (fire bursts)
     - FAERIES (freeze your foes!)
     - SLIMES (reproduce over and over,
       and overwhelm your enemies)
     - ORCS (an even more powerful
       grunt)
     - GHOSTS (fly through walls and
       scare your enemies)
     - SKELETONS (really fast; tunnel
       underground)
  *  Access to the nifty cheat codes
  *  The ability to jump to any level

  Registration is only $15 for a
diskette package or $10 for an
electronic-only copy (see readme.txt),
and will allow you to get free
upgrades for as long as Gladiator
improves. To register by check, send
your payment and address to:

    Gladiator v 3.8I REGISTRATION
    c/o Tom Ricket
    12645 Cambridge Drive
    Saratoga, CA  95070

  When making out your check, please
make it out to Tom Ricket, as the bank
may not want to cash it for us
otherwise.  If you have an e-mail
address, send that along as well and
we will notify you of upgrades more
quickly.

  You can also register online, with
a credit card, by visiting our site at
http://www.fsgames.com/glad/greg.html
and clicking the 'Get it now!'
button.

  The current, FREEWARE version of
Gladiator should always be availible
at our home page:
 http://www.fsgames.com/glad/

  Again, thank you for playing
Gladiator; we hope you enjoy it!
Even if you don't want to register,
please send us your bug reports and
other feedback!  We also appreciate
knowing where you found Gladiator
(web site, Aol, BBS, etc.).
You can send e-mail to:
    
    tricket@fsgames.com
          or
    support@fsgames.com

